checkData

### 2023-08-29 analysis/checkData.Rmd
corrected csv names

dj_prominent <- read_csv(here('data','raw', 'journalList_PROMINENT.csv')) %>% #loads csv of googlesheet data of prominent journals
  slice_head(n = 114) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

dj_random <- read_csv(here('data','raw', 'journalList_RANDOM.csv')) %>% #loads csv of googlesheet data of random journals
  slice_head(n = 108) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

>>>>

dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
  slice_head(n = 114) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
  slice_head(n = 108) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )
